### 2016-10-24 sec-related-work.tex
Add citations for HMMs to related work section.

>>>>

Our model is based heavily upon the prior art of Hidden Markov
Models~\cite{Rabiner:1990:RSR} for sequence labeling tasks. These types of
models are widely applicable and have been used for tasks such as speech
recognition~\cite{Huang:1990:HMM} and part-of-speech
tagging~\cite{Jurafsky:2009:SLP}. We employ maximum likelihood estimation
for estimating our model parameters using the EM algorithm
framework~\cite{Dempster:1977:JRSS} by modifying the Baum-Welch algorithm
for traditional HMMs~\cite{Rabiner:1990:RSR}.
